### 2020-03-05 short.body.tex
Fiddling

\begin{figure*}[b!]
\begin{center}
\includegraphics[width=0.4\textwidth]{figures/figheatmap_seird_noname.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.44\textwidth]{figures/figheatmap_seirdR0_noname.pdf}\\
\mbox{}\\
\includegraphics[width=0.4\textwidth]{figures/figheatmap_seird_2_noname.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.44\textwidth]{figures/figheatmap_seird_R02_noname.pdf}
\caption{Relevance of asymptomatic transmission given variation in
relative transmission and probability that a given, newly infected individual is asymptomatic.  (Top) Long duration asymptomatic cases increase ${\cal{R}}_0$ with increasing relevance.
(Bottom) Short duration asymptomatic cases decrease ${\cal{R}}_0$ with increasing relevance.
Technically, renewal equations provide a route to connect
observed increases in case counts, i.e., ${\cal{R}}_0 = \frac{1}{M(-r)}$
where $M(-r)=\int_0^{\infty}\mathrm{d} a e^{-ra}g(a)$.
For the present model,
$M(r)=qM_E(-r)M_{I_a}(-r)+(1-q)M_E(-r)M_{I_s}(-r)$
where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
and $q$ is the fraction of realized new secondary cases caused by
asymptomatic individuals.  In all of these heatmaps, $\gamma_e=1/4$,
$\gamma_s=1/10$, and $r=1/7$. Here, the average duration
in symptomatic and asymptomatic states are $T_s=1/\gamma_s$ and 
$T_a=1/\gamma_a$, respectively. Here the filled circle denotes ${\cal{R}}_0\approx 3.12$
in the event of $p=0$ and $\beta_a=0$, and the open symbols are for $\beta_a/\beta_s=0.5$ and 
$p=0.5$ and $p=0.9$ for reference.
%Renewal equations provide a route to connect
%observed increases in case counts, i.e.,
%\begin{equation}
%{\cal{R}}_0 = \frac{1}{M(-r)}
%\end{equation}
%where $r$ is the speed of the disease spread and 
%$M(r)$ is related to 
%$g(a)$ (the normalized age of transmission) such that 
%\begin{equation}
%M(r)=\int_0^{\infty}\mathrm{d} a e^{ra}g(a).
%\end{equation}
%For the present model, the moment generating function is
%\begin{equation}
%M(r)=qM_E(r)M_{I_a}(r)+(1-q)M_E(r)M_{I_s}(r)
%\end{equation}
%where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
%$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
%$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
%and $q$ is the fraction of realized new secondary cases caused by
%asymptomatic individuals. 
%The relevance $q$ is an unknown feature of
\label{fig.relevance}}
\end{center}
\end{figure*}

>>>>

\begin{figure*}[b!]
\begin{center}
\includegraphics[width=0.4\textwidth]{group/figheatmap_seird_noname.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.44\textwidth]{group/figheatmap_seirdR0_noname.pdf}\\
\mbox{}\\
\includegraphics[width=0.4\textwidth]{group/figheatmap_seird_2_noname.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.44\textwidth]{group/figheatmap_seird_R02_noname.pdf}
\caption{Relevance of asymptomatic transmission given variation in
relative transmission and probability that a given, newly infected individual is asymptomatic.  (Top) Long duration asymptomatic cases increase ${\cal{R}}_0$ with increasing relevance.
(Bottom) Short duration asymptomatic cases decrease ${\cal{R}}_0$ with increasing relevance.
Technically, renewal equations provide a route to connect
observed increases in case counts, i.e., ${\cal{R}}_0 = \frac{1}{M(-r)}$
where $M(-r)=\int_0^{\infty}\mathrm{d} a e^{-ra}g(a)$.
For the present model,
$M(r)=qM_E(-r)M_{I_a}(-r)+(1-q)M_E(-r)M_{I_s}(-r)$
where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
and $q$ is the fraction of realized new secondary cases caused by
asymptomatic individuals.  In all of these heatmaps, $\gamma_e=1/4$,
$\gamma_s=1/10$, and $r=1/7$. Here, the average duration
in symptomatic and asymptomatic states are $T_s=1/\gamma_s$ and 
$T_a=1/\gamma_a$, respectively. Here the filled circle denotes ${\cal{R}}_0\approx 3.12$
in the event of $p=0$ and $\beta_a=0$, and the open symbols are for $\beta_a/\beta_s=0.5$ and 
$p=0.5$ and $p=0.9$ for reference.
%Renewal equations provide a route to connect
%observed increases in case counts, i.e.,
%\begin{equation}
%{\cal{R}}_0 = \frac{1}{M(-r)}
%\end{equation}
%where $r$ is the speed of the disease spread and 
%$M(r)$ is related to 
%$g(a)$ (the normalized age of transmission) such that 
%\begin{equation}
%M(r)=\int_0^{\infty}\mathrm{d} a e^{ra}g(a).
%\end{equation}
%For the present model, the moment generating function is
%\begin{equation}
%M(r)=qM_E(r)M_{I_a}(r)+(1-q)M_E(r)M_{I_s}(r)
%\end{equation}
%where each of the component functions are $M_E(-r)=\frac{\gamma_e}{\gamma_e+r}$,
%$M_{I_a}(-r)=\frac{\gamma_a}{\gamma_a+r}$, 
%$M_{I_s}(-r)=\frac{\gamma_s}{\gamma_s+r}$,
%and $q$ is the fraction of realized new secondary cases caused by
%asymptomatic individuals. 
%The relevance $q$ is an unknown feature of
\label{fig.relevance}}
\end{center}
\end{figure*}
